---
title: "Sweetgum Genetic Study"

knit: (function(input_file, encoding) {
    out_dir <- 'docs';
    rmarkdown::render(input_file,
      encoding = encoding,
      output_file=file.path(dirname(input_file), out_dir, 'index.html'))})

author: "Andrea De Stefano"
date: "2023-12-01"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 10, fig.height = 8, fig.align = "left")
```
# General info {.tabset}

I created this website to track the progress with the sweetgum genetic study.

There are 7 parts:

1. Libraries, dataset loading, and data wrangling.
2. SAS code.
3. Survival rate plots.
4. Groundline diameter (GLD) plots and stats.
5. Tree height plots and stats.
6. DBH plots and stats.
7. Live crown height plots and stats.

## Data Wrangling {.tabset}

```{r, echo = TRUE}

library(tidyverse)
library(ggpubr)
library(plotly)

hane_crown <- read.csv("https://raw.githubusercontent.com/azd169/R-datasets/main/hane_crown.csv",
                       header = T)
hane_gld <- read.csv("https://raw.githubusercontent.com/azd169/R-datasets/main/hane_gld.csv",
                       header = T)
hane_dbh <- read.csv("https://raw.githubusercontent.com/azd169/R-datasets/main/hane_dbh.csv",
                       header = T)
hane_ht <- read.csv("https://raw.githubusercontent.com/azd169/R-datasets/main/hane_ht.csv",
                       header = T)
hane_survival_year <- read.csv("https://raw.githubusercontent.com/azd169/R-datasets/main/hane_survival_year.csv",
                       header = T)
hane_survival_year_family <- read.csv("https://raw.githubusercontent.com/azd169/R-datasets/main/hane_survival_year_family.csv",
                       header = T)
hane_survival_year_location <- read.csv("https://raw.githubusercontent.com/azd169/R-datasets/main/hane_survival_year_location.csv",
                       header = T)
hane_survival_year_location_family <- read.csv("https://raw.githubusercontent.com/azd169/R-datasets/main/hane_survival_year_location_family.csv",
                       header = T)

hane_crown <- hane_crown %>%
  mutate(Year = fct_relevel(Year, c("Fifth", "Sixth", "Seventh")))

hane_gld <- hane_gld %>%
  mutate(Year = fct_relevel(Year, c("Initial", "First", "Second")))

hane_dbh <- hane_dbh %>%
  mutate(Year = fct_relevel(Year, c("Third", "Fourth", "Fifth", "Sixth", "Seventh")))

hane_ht <- hane_ht %>%
  mutate(Year = fct_relevel(Year, c("Initial", "First", "Second", "Third", "Fourth", "Fifth", "Sixth", "Seventh")))

hane_survival_year <- hane_survival_year %>%
  mutate(Year = fct_relevel(Year, c("Initial", "First", "Second")))

hane_survival_year_family <- hane_survival_year_family %>%
  mutate(Year = fct_relevel(Year, c("Initial", "First", "Second")))

hane_survival_year_location <- hane_survival_year_location %>%
  mutate(Year = fct_relevel(Year, c("Initial", "First", "Second")))

hane_survival_year_location_family <- hane_survival_year_location_family %>%
  dplyr::mutate(ID = paste(Location, Year, sep = ", ")) %>%
  mutate(ID = fct_relevel(ID, c("Hill Farm, Initial", "Hill Farm, First", "Hill Farm, Second",
                                "LA Tech, Initial", "LA Tech, First", "LA Tech, Second")))

```

## SAS Code {.tabset}

Procedure:

External trees were removed from the analysis and all the Variables were averaged at plot level.
A unique ID was created combining Genotype, Location, and Block (GLD in the SAS code)

Datasets used:

1. WORK.DBH for DBH
2. WORK.GLD for GLD
3. WORK.HEIGHT for tree height
4. WORK.CROWN for crown height

Here are the SAS models:

1. GLD

PROC GLIMMIX DATA = GLD H PLOTS = ALL;
CLASS Year Location Block Family GLB;
MODEL GLD = Year|Location|Family / SOLUTION DDFM = KR;
RANDOM intercept / SOLUTION SUBJECT = GLB TYPE = AR(1) CL;
LSMEANS Location Family Year * Location Year * Family/ ADJUST = TUKEY LINES;
ODS GRAPHICS OFF;
RUN;

2. Height

PROC GLIMMIX DATA = HEIGHT H PLOTS = ALL;
CLASS Year Location Block Family GLB;
MODEL Height = Year|Location|Family / SOLUTION DDFM = KR;
RANDOM intercept / SOLUTION SUBJECT = GLB TYPE = AR(1) CL;
LSMEANS Family/ ADJUST = TUKEY LINES;
SLICE Year * Location / SLICEBY = Year ADJUST = TUKEY LINES DIFF;
SLICE Year * Family / SLICEBY = Year ADJUST = TUKEY LINES DIFF;
ODS GRAPHICS OFF;
RUN;

3. DBH

PROC GLIMMIX DATA = DBH H PLOTS = ALL;
CLASS Year Location Block Family GLB;
MODEL DBH = Year|Location|Family / SOLUTION DDFM = KR;
RANDOM intercept / SOLUTION SUBJECT = GLB TYPE = AR(1) CL;
LSMEANS Family/ ADJUST = TUKEY LINES;
SLICE Year * Location / SLICEBY = Year ADJUST = TUKEY LINES DIFF;
SLICE Year * Family / SLICEBY = Year ADJUST = TUKEY LINES DIFF;
ODS GRAPHICS OFF;
RUN;

4. Crown Height

PROC GLIMMIX DATA = CROWN H PLOTS = ALL;
CLASS Year Location Block Family GLB;
MODEL CROWN = Year|Location|Family / SOLUTION DDFM = KR;
RANDOM intercept / SOLUTION SUBJECT = GLB TYPE = AR(1) CL;
LSMEANS Family/ ADJUST = TUKEY LINES;
SLICE Year * Location / SLICEBY = Year ADJUST = TUKEY LINES DIFF;
SLICE Year * Family / SLICEBY = Year ADJUST = TUKEY LINES DIFF;
ODS GRAPHICS OFF;
RUN;

## Survival rates {.tabset}

```{r, echo = TRUE}

Sur1 <- ggplot(hane_survival_year,
               aes(x = Survival, y = Rate, fill = Survival, Color = Survival)) +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 100), breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("green4", "red3"), 0.5)) +
  labs(title = "Survival Rate by Growing Season") +
  xlab("") +
  ylab("Survival rate (%)") +
  facet_wrap( ~ Year) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Sur1)

Sur2 <- ggplot(hane_survival_year_family,
               aes(x = Family, y = Rate, fill = Survival, color = Survival)) +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 100), breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("green4", "red3"), 0.5)) +
  labs(title = "Survival Rate by Growing Season and Family") +
  xlab("") +
  ylab("Survival rate (%)") +
  facet_wrap( ~ Year) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Sur2)

Sur3 <- ggplot(hane_survival_year_location,
               aes(x = Location, y = Rate, fill = Survival, Color = Survival)) +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 100), breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("green4", "red3"), 0.5)) +
  labs(title = "Survival Rate by Growing Season and Location") +
  xlab("") +
  ylab("Survival rate (%)") +
  facet_wrap( ~ Year) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Sur3)

Sur4 <- ggplot(hane_survival_year_location_family,
               aes(x = Family, y = Rate, fill = Survival, color = Survival)) +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 100), breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("green4", "red3"), 0.5)) +
  labs(title = "Survival Rate by Growing Season, Location, and Family") +
  xlab("") +
  ylab("Survival rate (%)") +
  facet_wrap( ~ ID, ncol = 3) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Sur4)

```

## GLD {.tabset}

```{r, echo = TRUE}

Fig1 <- ggplot(hane_gld,
                 aes(x = Family, y = GLD, fill = Family, color = Family)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 60), breaks = c(0, 10, 20, 30, 40, 50, 60), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  labs(title = "GLD: Family Effect") +
  xlab("Family") +
  ylab("GLD (mm)") +
  annotate("text",
           x = c(1, 2, 3, 4, 5, 6),
           y = c(50),
           label = c("b", "ab", "a", "a", "ab", "ab")) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Fig1)

Fig2 <- ggplot(hane_gld,
               aes(x = Year, y = GLD, fill = Location, color = Location)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", position = position_dodge(0.9), width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 70), breaks = c(0, 10, 20, 30, 40, 50, 60, 70), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#000000", "#999999"), 0.5)) +
  labs(title = "GLD: Year * Location") +
  xlab("Growing Season") +
  ylab("GLD (mm)") +
  annotate("text",
           x = c(1.78, 2.22, 2.78, 3.22),
           y = c(20, 20, 55, 50),
           label = c("b", "a", "a", "b")) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Fig2)

Fig3 <- ggplot(hane_gld,
               aes(x = Year, y = GLD, fill = Family, color = Family)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", position = position_dodge(0.9), width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 80), breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                               "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  labs(title = "GLD: Year * Family") +
  xlab("Growing Season") +
  ylab("GLD (mm)") +
  annotate("text",
           x = c(2.62, 2.78, 2.93, 3.08, 3.22, 3.38),
           y = c(45, 50, 55, 60, 55, 55),
           label = c("b", "b", "a", "a", "a", "a")) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Fig3)

```

## Height {.tabset}

```{r, echo = TRUE}

Fig4 <- ggplot(hane_ht,
               aes(x = Family, y = Height, fill = Family, color = Family)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 12), breaks = c(0, 2, 4, 6, 8, 10, 12), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  labs(title = "Height: Year * Location") +
  xlab("Family") +
  ylab("Height (m)") +
  annotate("text",
           x = c(1, 2, 3, 4, 5, 6),
           y = c(10),
           label = c("d", "cd", "a", "a", "bc", "ab")) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Fig4)

Fig5 <- ggplot(hane_ht,
                  aes(x = Year, y = Height, fill = Location, color = Location)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", position = position_dodge(0.9), width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 12), breaks = c(0, 2, 4, 6, 8, 10, 12), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#000000", "#999999"), 0.5)) +
  labs(title = "Height: Year * Location" ) +
  xlab("Growing Season") +
  ylab("Height (m)") +
  annotate("text",
           x = c(3.78, 4.22, 4.78, 5.22, 5.78, 6.22, 6.78, 7.22),
           y = c(5, 4, 7, 5.5, 8.5, 7.5, 11, 7.5),
           label = c("a", "b", "a", "b", "a", "b", "a", "b")) +
  theme_classic()

plotly::ggplotly(Fig5)

Fig6 <- ggplot(hane_ht,
               aes(x = Year, y = Height, fill = Family, color = Family)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", position = position_dodge(0.9), width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 12), breaks = c(0, 2, 4, 6, 8, 10, 12), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  labs(title = "Height: Year * Family") +
  xlab("Growing Season") +
  ylab("Height (m)") +
  annotate("text",
           x = c(2.63, 2.77, 2.92, 3.06, 3.22, 3.38,
                 3.63, 3.77, 3.92, 4.06, 4.22, 4.38,
                 4.63, 4.77, 4.92, 5.06, 5.22, 5.38,
                 5.63, 5.77, 5.92, 6.06, 6.22, 6.38,
                 6.63, 6.77, 6.92, 7.06, 7.22, 7.38,
                 7.63, 7.77, 7.92, 8.06, 8.22, 8.38
                 ),
           y = c(2.2, 2.5, 3, 3.3, 2.7, 2.9,
                 3.1, 3.3, 4.3, 4.5, 3.7, 3.9,
                 5, 5.5, 6.5, 6.8, 5.9, 6.2,
                 6.5, 7, 8.1, 8.4, 7.4, 7.8,
                 7.7, 8.5, 10.4, 10.4, 9.8, 10.2,
                 9.3, 9.2, 10.5, 10.4, 10, 10.3
                 ),
           label = c("c", "bc", "a", "a", "abc", "ab",
                     "c", "bc", "a", "a", "bc", "ab",
                     "d", "cd", "ab", "a", "bc", "ab",
                     "c", "bc", "a", "a", "b", "a",
                     "c", "c", "a", "a", "b", "ab",
                     "dc", "d", "a", "a", "bc", "ab"
                     )) +
  theme_classic()

plotly::ggplotly(Fig6)

```

## DBH {.tabset}

```{r, echo = TRUE}

Fig7 <- ggplot(hane_dbh,
               aes(x = Family, y = DBH, fill = Family, color = Family)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 20), breaks = c(0, 5, 10, 15, 20), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  labs(title = "DBH: Family Effect") +
  xlab("Family") +
  ylab("DBH (cm)") +
  annotate("text",
           x = c(1, 2, 3, 4, 5, 6),
           y = c(15),
           label = c("d", "cd", "b", "b", "cb", "a")) +
  theme_classic()

plotly::ggplotly(Fig7)

Fig8 <- ggplot(hane_dbh,
               aes(x = Year, y = DBH, fill = Location, color = Location)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", position = position_dodge(0.9), width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 20), breaks = c(0, 5, 10, 15, 20), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#000000", "#999999"), 0.5)) +
  labs(title = "DBH: Year * Location" ) +
  xlab("Growing Season") +
  ylab("DBH (cm)") +
  annotate("text",
           x = c(0.78, 1.22, 1.78, 2.22, 2.78, 3.22, 3.78, 4.22, 4.78, 5.22),
           y = c(5, 4, 8, 7, 11, 10, 13, 12, 14, 13),
           label = c("a", "b", "a", "b", "a", "b", "a", "b", "a", "b")) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Fig8)

Fig9 <- ggplot(hane_dbh,
               aes(x = Year, y = DBH, fill = Family, color = Family)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", position = position_dodge(0.9), width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 20), breaks = c(0, 5, 10, 15, 20), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  labs(title = "DBH: Year * Family") +
  xlab("Growing Season") +
  ylab("DBH (cm)") +
  annotate("text",
           x = c(0.63, 0.77, 0.92, 1.06, 1.22, 1.38,
                 1.63, 1.77, 1.92, 2.06, 2.22, 2.38,
                 2.63, 2.77, 2.92, 3.06, 3.22, 3.38,
                 3.63, 3.77, 3.92, 4.06, 4.22, 4.38,
                 4.63, 4.77, 4.92, 5.06, 5.22, 5.38
           ),
           y = c(3.2, 3.5, 5, 5.3, 4.7, 4.9,
                 6.1, 6.3, 7.8, 7.9, 7.5, 8.5,
                 8.9, 9.3, 10.1, 10.2, 10.8, 11.8,
                 11.1, 11.3, 11.9, 12.3, 12.8, 13.2,
                 12.7, 12.7, 12.9, 13.1, 13.5, 14.7
           ),
           label = c("c", "c", "ab", "a", "bc", "a",
                     "d", "cd", "b", "b", "bc", "a",
                     "c", "c", "b", "b", "b", "a",
                     "d", "cd", "bcd", "bc", "b", "a",
                     "b", "b", "b", "b", "b", "a"
           )) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Fig9)

```

## Crown {.tabset}

```{r, echo = TRUE}

Fig10 <- ggplot(hane_crown,
                aes(x = Family, y = Crown, fill = Family, color = Family)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 10), breaks = c(0, 2, 4, 6, 8, 10), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  labs(title = "Crown Height: Family Effect") +
  xlab("Family") +
  ylab("Crown Height (m)") +
  annotate("text",
           x = c(1, 2, 3, 4, 5, 6),
           y = c(8),
           label = c("b", "b", "a", "a", "a", "a")) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Fig10)

Fig11 <- ggplot(hane_crown,
               aes(x = Year, y = Crown, fill = Location, color = Location)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", position = position_dodge(0.9), width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 10), breaks = c(0, 2, 4, 6, 8, 10), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#000000", "#999999"), 0.5)) +
  labs(title = "Crown Height: Year * Location" ) +
  xlab("Growing Season") +
  ylab("Crown Height (m)") +
  annotate("text",
           x = c(0.78, 1.22, 1.78, 2.22, 2.78, 3.22),
           y = c(3.2, 1.7, 6.5, 4, 7.3, 5),
           label = c("a", "b", "a", "b", "a", "b")) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Fig11)

Fig12 <- ggplot(hane_crown,
               aes(x = Year, y = Crown, fill = Family, color = Family)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", position = position_dodge(0.9), width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 10), breaks = c(0, 2, 4, 6, 8, 10), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  labs(title = "Crown Height: Year * Family") +
  xlab("Growing Season") +
  ylab("Crown Height (m)") +
  annotate("text",
           x = c(1.63, 1.77, 1.92, 2.06, 2.22, 2.36,
                 2.63, 2.77, 2.92, 3.06, 3.22, 3.36
           ),
           y = c(2.5, 3.4, 6, 6.5, 5.5, 5.7,
                 4, 3.9, 7.2, 7.3, 6.1, 6.6
           ),
           label = c("b", "b", "a", "a", "a", "a",
                     "b", "b", "a", "a", "a", "a"
           )) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Fig12)

```