---
title: "Sweetgum Genetic Study"

knit: (function(input_file, encoding) {
    out_dir <- 'docs';
    rmarkdown::render(input_file,
      encoding = encoding,
      output_file = file.path(dirname(input_file), out_dir, 'index.html'))})

author: "Andrea De Stefano"
date: "2023-12-01"
output: html_document
---


```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, fig.width = 10, fig.height = 8, fig.align = "left")

```
# General info {.tabset}

I created this website to track the progress with the sweetgum genetic study.

All is contained in the following tabs:

1. Groundline diameter (GLD) SAS code and output.
2. Tree height SAS code and output.
3. DBH SAS code and output.
4. Crown height SAS code and output.
5. Survival rate plots.
6. GLD plots and stats.
7. Tree height plots and stats.
8. DBH plots and stats.
9. Live crown height plots and stats.

External trees were removed from the analysis and all the Variables were averaged at plot level. A unique ID was created for each tree combining Genotype, Location, and Block (GLD in the SAS code).


```{r, echo = F, warning = F, include = F}

library(tidyverse)
library(ggpubr)
library(plotly)
library(htmltools)

hane_crown <- read.csv("https://raw.githubusercontent.com/azd169/R-datasets/main/hane_crown.csv",
                       header = T)
hane_gld <- read.csv("https://raw.githubusercontent.com/azd169/R-datasets/main/hane_gld.csv",
                       header = T)
hane_dbh <- read.csv("https://raw.githubusercontent.com/azd169/R-datasets/main/hane_dbh.csv",
                       header = T)
hane_ht <- read.csv("https://raw.githubusercontent.com/azd169/R-datasets/main/hane_ht.csv",
                       header = T)
hane_survival_year <- read.csv("https://raw.githubusercontent.com/azd169/R-datasets/main/hane_survival_year.csv",
                       header = T)
hane_survival_year_family <- read.csv("https://raw.githubusercontent.com/azd169/R-datasets/main/hane_survival_year_family.csv",
                       header = T)
hane_survival_year_location <- read.csv("https://raw.githubusercontent.com/azd169/R-datasets/main/hane_survival_year_location.csv",
                       header = T)
hane_survival_year_location_family <- read.csv("https://raw.githubusercontent.com/azd169/R-datasets/main/hane_survival_year_location_family.csv",
                       header = T)

hane_crown <- hane_crown %>%
  mutate(Year = fct_relevel(Year, c("Fifth", "Sixth", "Seventh")))

hane_gld <- hane_gld %>%
  mutate(Year = fct_relevel(Year, c("Initial", "First", "Second")))

hane_dbh <- hane_dbh %>%
  mutate(Year = fct_relevel(Year, c("Third", "Fourth", "Fifth", "Sixth", "Seventh")))

hane_ht <- hane_ht %>%
  mutate(Year = fct_relevel(Year, c("Initial", "First", "Second", "Third", "Fourth", "Fifth", "Sixth", "Seventh")))

hane_survival_year <- hane_survival_year %>%
  mutate(Year = fct_relevel(Year, c("Initial", "First", "Second")))

hane_survival_year_family <- hane_survival_year_family %>%
  mutate(Year = fct_relevel(Year, c("Initial", "First", "Second")))

hane_survival_year_location <- hane_survival_year_location %>%
  mutate(Year = fct_relevel(Year, c("Initial", "First", "Second")))

hane_survival_year_location_family <- hane_survival_year_location_family %>%
  dplyr::mutate(ID = paste(Location, Year, sep = ", ")) %>%
  mutate(ID = fct_relevel(ID, c("Hill Farm, Initial", "Hill Farm, First", "Hill Farm, Second",
                                "LA Tech, Initial", "LA Tech, First", "LA Tech, Second")))

```


## GLD SAS {.tabset}

**CODE:** \
 \
PROC GLIMMIX DATA = GLD; \
CLASS Year Location Block Family GLB; \
MODEL GLD = Year|Location|Family / DDFM = KR; \
RANDOM intercept / SUBJECT = GLB TYPE = AR(1); \
LSMEANS Family / ADJUST = TUKEY LINES; \
SLICE Year * Location / SLICEBY = Year ADJUST = TUKEY LINES; \
SLICE Year * Family / SLICEBY = Year ADJUST = TUKEY LINES; \
ODS GRAPHICS OFF; \
RUN; \


**OUTPUT:** \

```{r, echo = F, warning = T}

htmltools::tags$iframe(
  src = base64enc::dataURI(file = "https://raw.githubusercontent.com/azd169/SAS_outputs/main/hane-results-GLD.html",
                           mime = "text/html; charset = UTF-8"),
  style = "border:0; position:relative; top:0; left:0; right:0; bottom:0; width:100%; height:3000px")

```

## Height SAS {.tabset}

**CODE: ** \
 \
PROC GLIMMIX DATA = HEIGHT; \
CLASS Year Location Block Family GLB; \
MODEL Height = Year|Location|Family / DDFM = KR; \
RANDOM intercept / SUBJECT = GLB TYPE = AR(1); \
LSMEANS Family / ADJUST = TUKEY LINES; \
SLICE Year * Location / SLICEBY = Year ADJUST = TUKEY LINES; \
SLICE Year * Family / SLICEBY = Year ADJUST = TUKEY LINES; \
ODS GRAPHICS OFF; \
RUN; \

**OUTPUT: **

```{r, echo = F, warning = F}

htmltools::tags$iframe(
  src = base64enc::dataURI(file = "https://raw.githubusercontent.com/azd169/SAS_outputs/main/hane-results-height.html",
                           mime = "text/html; charset = UTF-8"),
  style = "border:0; position:relative; top:0; left:0; right:0; bottom:0; width:100%; height:3000px")

```

## DBH SAS {.tabset}

**CODE: ** \
 \
PROC GLIMMIX DATA = DBH; \
CLASS Year Location Block Family GLB; \
MODEL DBH = Year|Location|Family / DDFM = KR; \
RANDOM intercept / SUBJECT = GLB TYPE = AR(1); \
LSMEANS Family / ADJUST = TUKEY LINES; \
SLICE Year * Location / SLICEBY = Year ADJUST = TUKEY LINES; \
SLICE Year * Family / SLICEBY = Year ADJUST = TUKEY LINES; \
ODS GRAPHICS OFF; \
RUN; \

**OUTPUT: **

```{r, echo = F, warning = F}

htmltools::tags$iframe(
  src = base64enc::dataURI(file = "https://raw.githubusercontent.com/azd169/SAS_outputs/main/hane-results-DBH.html",
                           mime = "text/html; charset = UTF-8"),
  style = "border:0; position:relative; top:0; left:0; right:0; bottom:0; width:100%; height:3000px")

```

## Crown SAS {.tabset}

**CODE: ** \
 \
PROC GLIMMIX DATA = CROWN; \
CLASS Year Location Block Family GLB; \
MODEL Crown = Year|Location|Family / DDFM = KR; \
RANDOM intercept / SUBJECT = GLB TYPE = AR(1); \
LSMEANS Family / ADJUST = TUKEY LINES; \
SLICE Year * Location / SLICEBY = Year ADJUST = TUKEY LINES; \
SLICE Year * Family / SLICEBY = Year ADJUST = TUKEY LINES; \
ODS GRAPHICS OFF; \
RUN; \

**OUTPUT: **

```{r, echo = F, warning = F}

htmltools::tags$iframe(
  src = base64enc::dataURI(file = "https://raw.githubusercontent.com/azd169/SAS_outputs/main/hane-results-crown.html",
                           mime = "text/html; charset = UTF-8"),
  style = "border:0; position:relative; top:0; left:0; right:0; bottom:0; width:100%; height:3000px")

```

## Survival rates {.tabset}

```{r, echo = F, warning = F}

Sur1 <- ggplot(hane_survival_year,
               aes(x = Survival, y = Rate, fill = Survival, Color = Survival)) +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 100), breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("green4", "red3"), 0.5)) +
  scale_color_manual(values = alpha(c("green4", "red3"), 0.5)) +
  labs(title = "Survival Rate by Growing Season") +
  xlab("") +
  ylab("Survival rate (%)") +
  facet_wrap( ~ Year) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Sur1)

Sur2 <- ggplot(hane_survival_year_family,
               aes(x = Family, y = Rate, fill = Survival, color = Survival)) +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 100), breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("green4", "red3"), 0.5)) +
  scale_color_manual(values = alpha(c("green4", "red3"), 0.5)) +
  labs(title = "Survival Rate by Growing Season and Family") +
  xlab("") +
  ylab("Survival rate (%)") +
  facet_wrap( ~ Year) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Sur2)

Sur3 <- ggplot(hane_survival_year_location,
               aes(x = Location, y = Rate, fill = Survival, Color = Survival)) +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 100), breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("green4", "red3"), 0.5)) +
  scale_color_manual(values = alpha(c("green4", "red3"), 0.5)) +
  labs(title = "Survival Rate by Growing Season and Location") +
  xlab("") +
  ylab("Survival rate (%)") +
  facet_wrap( ~ Year) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Sur3)

Sur4 <- ggplot(hane_survival_year_location_family,
               aes(x = Family, y = Rate, fill = Survival, color = Survival)) +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 100), breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("green4", "red3"), 0.5)) +
  scale_color_manual(values = alpha(c("green4", "red3"), 0.5)) +
  labs(title = "Survival Rate by Growing Season, Location, and Family") +
  xlab("") +
  ylab("Survival rate (%)") +
  facet_wrap( ~ ID, ncol = 3) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Sur4)

```

## GLD {.tabset}

```{r, echo = F, warning = F}

Fig1 <- ggplot(hane_gld,
                 aes(x = Family, y = GLD, fill = Family, color = Family)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 60), breaks = c(0, 10, 20, 30, 40, 50, 60), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  scale_color_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  labs(title = "GLD: Family Effect") +
  xlab("Family") +
  ylab("GLD (mm)") +
  annotate("text",
           x = c(1, 2, 3, 4, 5, 6),
           y = c(35, 38, 42, 44, 39, 40),
           label = c("b", "ab", "a", "a", "ab", "ab")) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Fig1)

Fig2 <- ggplot(hane_gld,
               aes(x = Year, y = GLD, fill = Location, color = Location)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", position = position_dodge(0.9), width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 70), breaks = c(0, 10, 20, 30, 40, 50, 60, 70), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#000000", "#999999"), 0.5)) +
  scale_color_manual(values = alpha(c("#000000", "#999999"), 0.5)) +
  labs(title = "GLD: Year * Location") +
  xlab("Growing Season") +
  ylab("GLD (mm)") +
  annotate("text",
           x = c(1.78, 2.22, 2.78, 3.22),
           y = c(20, 20, 50, 55),
           label = c("b", "a", "a", "b")) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Fig2)

Fig3 <- ggplot(hane_gld,
               aes(x = Year, y = GLD, fill = Family, color = Family)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", position = position_dodge(0.9), width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 80), breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                               "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  scale_color_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  labs(title = "GLD: Year * Family") +
  xlab("Growing Season") +
  ylab("GLD (mm)") +
  annotate("text",
           x = c(2.62, 2.78, 2.93, 3.08, 3.22, 3.38),
           y = c(45, 50, 55, 60, 55, 55),
           label = c("b", "b", "a", "a", "a", "a")) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Fig3)

```

## Height {.tabset}

```{r, echo = F, warning = F}

Fig4 <- ggplot(hane_ht,
               aes(x = Family, y = Height, fill = Family, color = Family)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 12), breaks = c(0, 2, 4, 6, 8, 10, 12), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  scale_color_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  labs(title = "Height: Year * Location") +
  xlab("Family") +
  ylab("Height (m)") +
  annotate("text",
           x = c(1, 2, 3, 4, 5, 6),
           y = c(7, 7.5, 8.6, 8.7, 7.7, 8),
           label = c("d", "cd", "a", "a", "bc", "ab")) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Fig4)

Fig5 <- ggplot(hane_ht,
                  aes(x = Year, y = Height, fill = Location, color = Location)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", position = position_dodge(0.9), width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 12), breaks = c(0, 2, 4, 6, 8, 10, 12), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#000000", "#999999"), 0.5)) +
  scale_color_manual(values = alpha(c("#000000", "#999999"), 0.5)) +
  labs(title = "Height: Year * Location" ) +
  xlab("Growing Season") +
  ylab("Height (m)") +
  annotate("text",
           x = c(3.78, 4.22, 4.78, 5.22, 5.78, 6.22, 6.78, 7.22),
           y = c(4, 5, 5.5, 7, 7.5, 8.5, 7.5, 11),
           label = c("a", "b", "a", "b", "a", "b", "a", "b")) +
  theme_classic()

plotly::ggplotly(Fig5)

Fig6 <- ggplot(hane_ht,
               aes(x = Year, y = Height, fill = Family, color = Family)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", position = position_dodge(0.9), width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 12), breaks = c(0, 2, 4, 6, 8, 10, 12), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  scale_color_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  labs(title = "Height: Year * Family") +
  xlab("Growing Season") +
  ylab("Height (m)") +
  annotate("text",
           x = c(2.63, 2.77, 2.92, 3.06, 3.22, 3.38,
                 3.63, 3.77, 3.92, 4.06, 4.22, 4.38,
                 4.63, 4.77, 4.92, 5.06, 5.22, 5.38,
                 5.63, 5.77, 5.92, 6.06, 6.22, 6.38,
                 6.63, 6.77, 6.92, 7.06, 7.22, 7.38,
                 7.63, 7.77, 7.92, 8.06, 8.22, 8.38
                 ),
           y = c(2.2, 2.5, 3, 3.3, 2.7, 2.9,
                 3.1, 3.3, 4.3, 4.5, 3.7, 3.9,
                 5, 5.5, 6.5, 6.8, 5.9, 6.2,
                 6.5, 7, 8.1, 8.4, 7.4, 7.8,
                 7.7, 8.5, 10.4, 10.4, 9.8, 10.2,
                 9.3, 9.2, 10.5, 10.4, 10, 10.3
                 ),
           label = c("c", "bc", "a", "a", "abc", "ab",
                     "c", "bc", "a", "a", "bc", "ab",
                     "d", "cd", "ab", "a", "bc", "ab",
                     "c", "bc", "a", "a", "b", "a",
                     "c", "c", "a", "a", "b", "ab",
                     "dc", "d", "a", "a", "bc", "ab"
                     )) +
  theme_classic()

plotly::ggplotly(Fig6)

```

## DBH {.tabset}

```{r, echo = F, warning = F}

Fig7 <- ggplot(hane_dbh,
               aes(x = Family, y = DBH, fill = Family, color = Family)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 20), breaks = c(0, 5, 10, 15, 20), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  scale_color_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  labs(title = "DBH: Family Effect") +
  xlab("Family") +
  ylab("DBH (cm)") +
  annotate("text",
           x = c(1, 2, 3, 4, 5, 6),
           y = c(11, 11.1, 11.5, 11.8, 12, 14),
           label = c("d", "cd", "b", "b", "cb", "a")) +
  theme_classic()

plotly::ggplotly(Fig7)

Fig8 <- ggplot(hane_dbh,
               aes(x = Year, y = DBH, fill = Location, color = Location)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", position = position_dodge(0.9), width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 20), breaks = c(0, 5, 10, 15, 20), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#000000", "#999999"), 0.5)) +
  scale_color_manual(values = alpha(c("#000000", "#999999"), 0.5)) +
  labs(title = "DBH: Year * Location" ) +
  xlab("Growing Season") +
  ylab("DBH (cm)") +
  annotate("text",
           x = c(0.78, 1.22, 1.78, 2.22, 2.78, 3.22, 3.78, 4.22, 4.78, 5.22),
           y = c(4, 5, 7, 8, 10, 11, 12, 13, 13, 14),
           label = c("a", "b", "a", "b", "a", "b", "a", "b", "a", "b")) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Fig8)

Fig9 <- ggplot(hane_dbh,
               aes(x = Year, y = DBH, fill = Family, color = Family)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", position = position_dodge(0.9), width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 20), breaks = c(0, 5, 10, 15, 20), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  scale_color_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  labs(title = "DBH: Year * Family") +
  xlab("Growing Season") +
  ylab("DBH (cm)") +
  annotate("text",
           x = c(0.63, 0.77, 0.92, 1.06, 1.22, 1.38,
                 1.63, 1.77, 1.92, 2.06, 2.22, 2.38,
                 2.63, 2.77, 2.92, 3.06, 3.22, 3.38,
                 3.63, 3.77, 3.92, 4.06, 4.22, 4.38,
                 4.63, 4.77, 4.92, 5.06, 5.22, 5.38
           ),
           y = c(3.2, 3.5, 5, 5.3, 4.7, 4.9,
                 6.1, 6.3, 7.8, 7.9, 7.5, 8.5,
                 8.9, 9.3, 10.1, 10.2, 10.8, 11.8,
                 11.1, 11.3, 11.9, 12.3, 12.8, 13.2,
                 12.7, 12.7, 12.9, 13.1, 13.5, 14.7
           ),
           label = c("c", "c", "ab", "a", "bc", "a",
                     "d", "cd", "b", "b", "bc", "a",
                     "c", "c", "b", "b", "b", "a",
                     "d", "cd", "bcd", "bc", "b", "a",
                     "b", "b", "b", "b", "b", "a"
           )) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Fig9)

```

## Crown {.tabset}

```{r, echo = F, warning = F}

Fig10 <- ggplot(hane_crown,
                aes(x = Family, y = Crown, fill = Family, color = Family)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 10), breaks = c(0, 2, 4, 6, 8, 10), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  scale_color_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  labs(title = "Crown Height: Family Effect") +
  xlab("Family") +
  ylab("Crown Height (m)") +
  annotate("text",
           x = c(1, 2, 3, 4, 5, 6),
           y = c(3, 3, 6, 6.5, 5, 5.5),
           label = c("b", "b", "a", "a", "a", "a")) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Fig10)

Fig11 <- ggplot(hane_crown,
               aes(x = Year, y = Crown, fill = Location, color = Location)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", position = position_dodge(0.9), width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 10), breaks = c(0, 2, 4, 6, 8, 10), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#000000", "#999999"), 0.5)) +
  scale_color_manual(values = alpha(c("#000000", "#999999"), 0.5)) +
  labs(title = "Crown Height: Year * Location" ) +
  xlab("Growing Season") +
  ylab("Crown Height (m)") +
  annotate("text",
           x = c(0.78, 1.22, 1.78, 2.22, 2.78, 3.22),
           y = c(1.7, 3.2, 4, 6.5, 5, 7.3),
           label = c("a", "b", "a", "b", "a", "b")) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Fig11)

Fig12 <- ggplot(hane_crown,
               aes(x = Year, y = Crown, fill = Family, color = Family)) +
  stat_summary(fun.data = mean_sd, geom = "errorbar", position = position_dodge(0.9), width = 0.2, color = "grey") +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  font("title", size = 22) +
  font("xlab", size = 18) +
  font("ylab", size = 18) +
  font("xy.text", size = 16) +
  scale_y_continuous(limits = c(0, 10), breaks = c(0, 2, 4, 6, 8, 10), expand = c(0,0)) +
  scale_fill_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  scale_color_manual(values = alpha(c("#E69F00", "#56B4E9", "#009E73",
                                     "#F0E442", "#D55E00", "#CC79A7"), 0.5)) +
  labs(title = "Crown Height: Year * Family") +
  xlab("Growing Season") +
  ylab("Crown Height (m)") +
  annotate("text",
           x = c(1.63, 1.77, 1.92, 2.06, 2.22, 2.36,
                 2.63, 2.77, 2.92, 3.06, 3.22, 3.36
           ),
           y = c(2.5, 3.4, 6, 6.5, 5.5, 5.7,
                 4, 3.9, 7.2, 7.3, 6.1, 6.6
           ),
           label = c("b", "b", "a", "a", "a", "a",
                     "b", "b", "a", "a", "a", "a"
           )) +
  guides(fill = "none") +
  theme_classic()

plotly::ggplotly(Fig12)

```